Different forms of uncertainty differently affect the evolution of social learning

### 2022-07-18 ms.tex
finished Model restruct
added intro results par

@@

\begin{figure}
  \caption{Social learning prevalence (y-axes) monotonically decreases as 
  environmental variabilty, $u$, increases (x-axes) in most uncertainty contexts. 
  Other uncertainty values $\pilow$ (rows), $B$ (columns), and $L$ (keys)
  shift and flatten the decrease from all-social-learner populations to all-asocial 
  populations.}
  \label{fig:mainResults}
  \centering
    \includegraphics[width=\textwidth]{Figures/mainResultsPlots.pdf}
\end{figure}

@@

\bibliographystyle{apacite}
\bibliography{/Users/mt/workspace/Writing/library.bib}
% \bibliography{this.bib}

>>>>

To understand how different forms of uncertainty interact to affect the evolution
of social learning, we measured simulated social learning prevalence across a 
suite of simulations over uncertainty parameters. We analyze simulation outcomes
by plotting the mean observed social learning frequency, $\meansl$ across all agents 
and 1000 simulation trials for each uncertainty parameter setting. We do not calculate
significance measures since these can be inflated by simply adding more trials.
Instead, we visualize and inspect plots with $\meansl$ on the y-axis and
environmental variability, $u$ on the x-axis. This is convenient because we are
most certain about how $\meansl$ depends on $u$: we expect $\meansl$ to decrease
as $u$ increases since environmental variability is well understood to cause
socially-transmitted information to become outdated. When the other forms of
uncertainty are varied, this causes changes to when and how quickly social learning
is suppressed as $u$ increases. To inspect these changes, we show nine plots
of $\meansl$ over $u$ in a 3x3 plot array (Figure~\ref{fig:mainResults}). 
Plot array columns correspond to different selection set sizes, $B$; rows
correspond to different non-optimal payoff values, $\pilow$ (recall optimal
payoff $\pihigh=0.9$ for all analyses); plot line and marker colors correspond
to different effective lifespan, $L$, values. 
We support our conclusions regarding the evolution of
social learning by analyzing the time to model 
fixation and by comparing the average net payoffs in our simulations to the
expected payoffs for individuals in both populations of all social learners
and in populations of all individual learners. We thus use our analysis 
to understand changes to how $\meansl$ changes over $u$ for different uncertainty parameter settings.

@@

\begin{figure}
  \caption{Social learning prevalence (y-axes) monotonically decreases as 
  environmental variabilty, $u$, increases (x-axes) in most uncertainty contexts. 
  Other uncertainty values $\pilow$ (rows), $B$ (columns), and $L$ (keys)
  shift and flatten the decrease from all-social-learner populations to all-asocial 
  populations.}
  \label{fig:mainResults}
  \centering
    \includegraphics[width=\textwidth]{{Figures/supplement/nagents=1000/mainResultsPlots.pdf}}
\end{figure}

@@

\bibliographystyle{apacite}
% \bibliography{/Users/mt/workspace/Writing/library.bib}
\bibliography{this.bib}
